Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-05-15 paper.tex
Added text on CDK devs and some associated refs

\address{%
    \iid(1)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(2)National Institute of Health, Somewhere in the US, USA \\
    \iid(3)... \\
    \iid(4)Kitware, Inc., 28 Corporate Drive, Clifton Park, NY 12065, USA \\
    \iid(5)Department of Chemistry, University of Pittsburgh, 219 Parkman Avenue, Pittsburgh, PA 15260, USA \\
    \iid(6)Gorlaeus Laboratories, Leiden University, 2333 CC Leiden, The Netherlands \\
    \iid(7)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK \\
    \iid(8)Unilever Centre for Molecular Sciences Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK \\
    \iid(9)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland \\
    \iid(10)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia \\
    \iid(11)... \\
    \iid(12)Department of Chemistry, University of Washington, Seattle, WA 98195 \\
    \iid(13)iChemLabs, 200 Centennial Ave., Suite 200, Piscataway, NJ 08854, USA \\
    \iid(14)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden
}%

@@

[Insert main focus of work on CDK in last 5 years]

>>>>

\address{%
    \iid(1)Department of Pharmaceutical Biosciences, Uppsala University, Box 591, 751 24 Uppsala, Sweden \\
    \iid(2)NIH Center for Translational Therapeutics, 9800 Medical  Center Drive, Rockville, MD 20878 \\
    \iid(3)... \\
    \iid(4)Kitware, Inc., 28 Corporate Drive, Clifton Park, NY 12065, USA \\
    \iid(5)Department of Chemistry, University of Pittsburgh, 219 Parkman Avenue, Pittsburgh, PA 15260, USA \\
    \iid(6)Gorlaeus Laboratories, Leiden University, 2333 CC Leiden, The Netherlands \\
    \iid(7)Cheminformatics and Metabolism Team, European Bioinformatics Institute (EBI), Wellcome Trust Genome Campus, Hinxton, Cambridge, UK \\
    \iid(8)Unilever Centre for Molecular Sciences Informatics, Department of Chemistry, University of Cambridge, Lensfield Road, CB2 1EW, UK \\
    \iid(9)Analytical and Biological Chemistry Research Facility, Cavanagh Pharmacy Building, University College Cork, College Road, Cork, Co. Cork, Ireland \\
    \iid(10)GGA Software Services LLC, 41 Nab. Chernoi rechki 194342, Saint Petersburg, Russia \\
    \iid(11)... \\
    \iid(12)Department of Chemistry, University of Washington, Seattle, WA 98195 \\
    \iid(13)iChemLabs, 200 Centennial Ave., Suite 200, Piscataway, NJ 08854, USA \\
    \iid(14)Division of Molecular Toxicology, Institute of Environmental Medicine, %
        Nobels vaeg 13, Karolinska Institutet, 171 77 Stockholm, Sweden
}%

@@

The CDK project has been under regular development over the last five
years. Several feature have been implemented ranging from core
components such as an extensible SMARTS matching system, new graph (\&
subgraph) isomorphism method \cite{smsd} to more application oriented
components such as 3D pharmacophore searching and matching, a variety
of structural key and hashed fingerprints. In addition, there have
been a number of second generation tools developed on top of the CDK
such as OrChem \cite{orchem} and PaDEL \cite{padel}. In addition to
the use of the CDK in various applications, it has been deployed in
the form of web services \cite{Dong:2007aa} and has formed the basis
of a variety of web applications.
